### 2013-11-02 NeurounitFrontiers/Paper.tex
Updated thru sec 3

  def run_test(self, model):
    inputs, means, stds = self.inputs, self.means, self.stds
    n = len(inputs)
    counts = numpy.empty((n,))
    for i in xrange(n):
      counts[i] = model.spike_count_from_current(inputs[i])
    chisquared = sum((counts-means)**2 / means) # An array of chi-squared values.  
    p = scipy.stats.chi2.cdf(chisquared,n-1) # An array of p-values.  
    pooled_p = sciunit.utils.fisherp(p_array) # A pooled p-value.  
    return sciunit.PValue(pooled_p, related_data={
      "inputs": inputs, "counts": counts, "obs_means": means, "obs_stds": stds
    })
\end{python}
\vspace{-5px}
\caption{A single neuron spike count test family implemented using \textit{SciUnit}. This family contains logic common to many different systems, so it is distributed in the \textit{NeuronUnit} repository (see Sec. \ref{sec:neuronunit}).}
\label{fig:rate_test}
\vspace{-15px}
\end{figure}

@@

%In many cases, models require no modifications to take the new tests because the same type of model output is being requested.
\subsection{Implementing a Validation Test in \textit{SciUnit}}
Fig. \ref{fig:rate_test} shows how a scientist would implement spike count tests such as the one described above using \textit{SciUnit}. 
A \textit{SciUnit} validation test is an {instance} (i.e. an object) of a Python class implementing the \verbx{sciunit.Test} interface (cf. line 1). 
Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor (constructors are named \verbx{__init__} in Python, lines 9-10). The meaning of each parameter along with a description of the goodness-of-fit metric used by the test is documented on lines 4-7. 
%For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
For example, given observations from hippocampal CA1 cells (not shown), we can instantiate a test as follows:
\begin{python}
  CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
\end{python}
We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided. 
As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data. 
For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} \cite{neurounit_url} (Sec. \ref{sec:neuronunit}).

Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{run_test} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
To specify the interface between the test and the model (that is, to specify an appropriate scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig. \ref{fig:rate_test}. 
Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java \cite{java_interfaces_url}. 
In Python, they are written as classes with unimplemented members. 
The capability required by the test in Fig. \ref{fig:rate_test} is shown in Fig. \ref{fig:capability}. 
In \textit{SciUnit}, classes defining capabilities are tagged as such by inheriting from \verbx{sciunit.Capability}. The test in Figure \ref{fig:rate_test} uses this capability on line 19 to produce a spike count prediction for each input current.

@@

\subsection{Models}
Capabilities are \emph{implemented} by models. In \textit{SciUnit}, models are instances of Python classes that inherit from \verbx{sciunit.Model}. Like tests, the class itself represents a family of models, parameterized by the arguments needed in the constructor. A particular model is an object created by supplying the parameters.

A simple {family} of models, \verb{LinearModel}, implementing the capability in Fig. \ref{fig:capability} as well as another capability shown in Fig. \ref{fig:training}, is shown in Fig. \ref{fig:simple_model}. 
Models in this family, \verbx{LinearModel}, produce a spike count by applying a linear transformation to the mean of the provided input current. 
The family is parameterized by a scale factor and offset, both scalars. 
To create a \emph{particular} model, the modeler may choose particular parameter values, just as with test families:
\begin{python}
CA1_linear_model_heuristic = LinearModel(3.0, 1.0)
\end{python}
Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
An alternative test design to the one in Fig. \ref{fig:rate_test} would add a second required capability (Fig. \ref{fig:training}) and a corresponding training phase to the \verb|run_test| method. 
This design would be relevant only for those models for which parameters can be adjusted without human involvement. 
Whether to build a training phase into the test protocol is a choice left to each modeler. 
Although Fig. \ref{fig:rate_test} does not include a training phase, if training data is available then models that nevertheless implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
\begin{python}
CA1_linear_model_fit = LinearModel()
CA1_linear_model_fit.train_with_currents(CA1_training_in, CA1_training_out)
\end{python}
\begin{figure}
\begin{python}
class LinearModel(sciunit.Model, SpikeCountFromCurrent, 
    TrainSpikeCountFromCurrent):
  def __init__(self, scale=None, offset=None): 
    self.scale, self.offset = scale, offset

@@

  def train_with_currents(self, currents, counts):
    means = [numpy.mean(c) for c in currents]
    [self.offset, self.scale] = numpy.polyfit(means, counts, deg=1)    
\end{python}
\caption{A simple model that returns a spike count by scaling the mean of the input by a fixed parameter.}
\label{fig:simple_model}
\vspace{-15px}
\end{figure}

Finally, a test is executed against a model instance, using the \verbx{sciunit.judge} function:
\begin{python}
score = sciunit.judge(CA1_sc_test, CA1_linear_model_heuristic)
\end{python}

Collection of tests with mutually coherent requirments, i.e. various summaries of the available empirical data, can form test suites.
The following is a test suite that could be used for a simplified version of the QSNMC:  
\begin{python}
CA1_suite = sciunit.TestSuite([CA1_sc_test, CA1_sl_test, CA1_sv_test, CA1_isi_test, CA1_ism_test])
\end{python}
When a test suite is executed against a model, it produces summary data that can be shown on the console or visualized by other tools, such as the web application described in Sec. \ref{sec:scidash}.

>>>>

  def _judge(self, model):
    inputs, means, stds = self.inputs, self.means, self.stds
    n = len(inputs)
    counts = numpy.empty((n,))
    for i in xrange(n):
      counts[i] = model.spike_count_from_current(inputs[i])
    chisquared = sum((counts-means)**2 / means) # An array of chi-squared values.  
    p = scipy.stats.chi2.cdf(chisquared,n-1) # An array of p-values.  
    pooled_p = sciunit.utils.fisherp(p_array) # A pooled p-value.  
    return sciunit.PValue(pooled_p, related_data={
      "inputs": inputs, "counts": counts, "obs_means": means, "obs_stds": stds
    })
\end{python}
\vspace{-5px}
\caption{A single neuron spike count test family implemented using \textit{SciUnit}. This family contains logic common to many different systems, so it is distributed in the \textit{NeuronUnit} repository (see Sec. \ref{sec:neuronunit}).}
\label{fig:rate_test}
\vspace{-15px}
\end{figure}

@@

%In many cases, models require no modifications to take the new tests because the same type of model output is being requested.
\subsection{Implementing a Validation Test in \textit{SciUnit}}
Fig. \ref{fig:rate_test} shows how a scientist would implement spike count tests such as the one described above using \textit{SciUnit}. 
A \textit{SciUnit} validation test is an {instance} (i.e. an object) of a Python class implementing the \verbx{sciunit.Test} interface (cf. line 1). 
Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor (constructors are named \verbx{__init__} in Python, lines 9-10). The meaning of each parameter along with a description of the goodness-of-fit metric used by the test is documented on lines 4-7. 
%For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
For example, given observations from hippocampal CA1 cells (not shown), we can instantiate a test as follows\todo{use iPython style In[0] notation?}:
\begin{python}
  CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
\end{python}
We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided. 
As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data. 
For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} \cite{neurounit_url} (Sec. \ref{sec:neuronunit}).

Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{_judge} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
To specify the interface between the test and the model (that is, to specify an appropriate scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig. \ref{fig:rate_test}. 
Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java \cite{java_interfaces_url}. 
In Python, they are written as classes with unimplemented members. 
The capability required by the test in Fig. \ref{fig:rate_test} is shown in Fig. \ref{fig:capability}. 
In \textit{SciUnit}, classes defining capabilities are tagged as such by inheriting from \verbx{sciunit.Capability}. The test in Figure \ref{fig:rate_test} uses this capability on line 19 to produce a spike count prediction for each input current.

@@

\subsection{Models}
Capabilities are \emph{implemented} by models. In \textit{SciUnit}, models are instances of Python classes that inherit from \verbx{sciunit.Model}. Like tests, the class itself represents a family of models, parameterized by the arguments of the constructor. A particular model is an instance of such a class.

Figure \ref{fig:simple_model} shows how to write a simple {family} of models, \verbx{LinearModel}, that implement the capability in Fig. \ref{fig:capability} as well as another capability shown in Fig. \ref{fig:training}, discussed below. 
Models in this family generate a spike count by applying a linear transformation to the mean of the provided input current. The family is parameterized by the scale factor and the offset of the transformation, both scalars. 
To create a \emph{particular} linear model, a modeler can provide particular parameter values, just as with test families:
\begin{python}
CA1_linear_model_heuristic = LinearModel(3.0, 1.0)
\end{python}
Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
An alternative test design would add a training phase where these parameters were fit to data using the capability shown in Fig. \ref{fig:training}. 
This test could thus only be used for those models for which parameters can be adjusted without human involvement. 
Whether to build a training phase into the test protocol is a choice left to each modeler. 
For example, Fig. \ref{fig:rate_test} does not include a training phase.

If training data is externally available, then models that nevertheless do implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
\begin{python}
CA1_linear_model_fit = LinearModel()
CA1_linear_model_fit.train_with_currents(CA1_training_in, CA1_training_out)
\end{python}
\begin{figure}
\begin{python}
class LinearModel(sciunit.Model, SpikeCountFromCurrent, 
    TrainSpikeCountFromCurrent):
  def __init__(self, scale=None, offset=None): 
    self.scale, self.offset = scale, offset

@@

  def train_with_currents(self, currents, counts):
    means = [numpy.mean(c) for c in currents]
    [self.offset, self.scale] = numpy.polyfit(means, counts, deg=1)    
\end{python}
\caption{A model that returns a spike count by applying a linear transformation to the mean input current. The parameters can be provided manually or learned from data provided by a test or user (see text).}
\label{fig:simple_model}
\vspace{-15px}
\end{figure}

\subsection{Executing Tests} A test is executed against a model using the \verbx{judge} method:
\begin{python}
score = CA1_sc_test.judge(CA1_linear_model_heuristic)
\end{python}

This method proceeds by first checking that the provided model implements all required capabilities. It then calls the test's \verbx{_judge} method to produce a score. A reference to the test and model are added to the score for convenience before it is ultimately returned to the user.

\subsection{Test Suites and Score Matrices} A collection of tests intended to be run on the same model can be put together to form a test suite.
The following is a test suite that could be used for a simplified version of the QSNMC:  
\begin{python}
CA1_suite = sciunit.TestSuite([CA1_sc_test, CA1_sl_test, CA1_sv_test, CA1_isi_test, CA1_ism_test])
\end{python}
Like a single test, a test suite is capable of judging one or more models. The result is a score matrix much like the one diagramed in Fig. \ref{fig:sciunit_overview}.
\begin{python}
CA1_matrix = CA1_suite.judge([CA1_linear_model_heuristic, CA1_linear_model_fit])
\end{python}
A simple summary of the scores in a score matrix can be printed to the console or  visualized by other tools, such as the web application \textit{SciDash} described in Sec. \ref{sec:scidash}.
